The GALEX View of ``Boyajian's Star''

### 2017-10-23 paper/paper.tex
move to AASTeX6.1

%\documentclass[twocolumn, trackchanges]{aastex6}
\documentclass[twocolumn]{aastex6}

@@

\author{
	James R. A. Davenport\altaffilmark{1,2},
	Kevin R. Covey\altaffilmark{1},
	Riley W. Clarke\altaffilmark{1}, \\
	Zachery Laycock\altaffilmark{1},
	Scott W. Fleming\altaffilmark{3},
	Tabetha S. Boyajian\altaffilmark{4},
	Benjamin T. Montet\altaffilmark{5,6},\\
	Bernie Shiao\altaffilmark{3},
	Chase C. Million\altaffilmark{7},
	David J. Wilson\altaffilmark{8},
	Manuel Olmedo\altaffilmark{9},
	Eric E. Mamajek\altaffilmark{10,11}\\
	Daniel Olmedo\altaffilmark{9}, 
	Miguel Ch\'{a}vez\altaffilmark{9},
	Emanuele Bertone\altaffilmark{9}
	}

\altaffiltext{1}{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}
\altaffiltext{2}{NSF Astronomy and Astrophysics Postdoctoral Fellow}
\altaffiltext{3}{STScI, 3700 San Martin Dr., Baltimore, MD 21218}
\altaffiltext{4}{Department of Physics and Astronomy, Louisiana State University, 261-A Nicholson Hall, Tower Dr, Baton Rouge, LA 70803}
\altaffiltext{5}{Department of Astronomy and Astrophysics, University of Chicago, 5640 S. Ellis Ave, Chicago, IL 60637, USA}
\altaffiltext{6}{NASA Sagan Fellow}
\altaffiltext{7}{Million Concepts LLC, PO Box 119, 141 Mary St, Lemont, PA 16851, USA}
\altaffiltext{8}{Department of Physics, University of Warwick, Coventry CV4 7AL, UK}
\altaffiltext{9}{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}
\altaffiltext{10}{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
\altaffiltext{11}{Department of Physics \& Astronomy, University of Rochester, Rochester, NY 14627, USA}

>>>>

%\documentclass[twocolumn, trackchanges]{aastex6}
\documentclass[twocolumn]{aastex61}

@@

\author{James. R. A. Davenport}
\affiliation{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}
\affiliation{NSF Astronomy and Astrophysics Postdoctoral Fellow}

\author{Kevin R. Covey}
\affiliation{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}

\author{Riley W. Clarke}
\affiliation{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}

\author{Zachery Laycock}
\affiliation{Department of Physics \& Astronomy, Western Washington University, 516 High St., Bellingham, WA 98225, USA}

\author{Scott W. Fleming}
\affiliation{STScI, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{Tabetha S. Boyajian}
\affiliation{Department of Physics and Astronomy, Louisiana State University, 261-A Nicholson Hall, Tower Dr, Baton Rouge, LA 70803, USA}

\author{Benjamin T. Montet}
\affiliation{Department of Astronomy and Astrophysics, University of Chicago, 5640 S. Ellis Ave, Chicago, IL 60637, USA}
\affiliation{NASA Sagan Fellow}

\author{Bernie Shiao}
\affiliation{STScI, 3700 San Martin Dr., Baltimore, MD 21218}

\author{Chase C. Million}
\affiliation{Million Concepts LLC, PO Box 119, 141 Mary St, Lemont, PA 16851, USA}

\author{David J. Wilson}
\affiliation{Department of Physics, University of Warwick, Coventry CV4 7AL, UK}

\author{Manuel Olmedo}
\affiliation{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}

\author{Eric E. Mamajek}
\affiliation{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
\affiliation{Department of Physics \& Astronomy, University of Rochester, Rochester, NY 14627, USA}

\author{Daniel Olmedo}
\affiliation{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}

\author{Miguel Ch\'{a}vez}
\affiliation{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}

\author{Emanuele Bertone}
\affiliation{Instituto Nacional de Astrof\'{i}sica Optica y Electr\'{o}nica, Tonantzintla, Puebla, M\'{e}xico}
